\documentclass{article}
% \usepackage[margin=2.5cm]{geometry}
\usepackage[margin=2cm, headheight=0pt, headsep=1cm]{geometry}
\usepackage{enumerate, fancyhdr, graphicx, amsmath, float, url, hyperref, color}

\title{Vault 5431 - Charter}
\author{Alicia Wu, Britney Wong, Chang Yang Jiao, Paul Chesnais}
\date{\today}

\pagestyle{fancy}
\fancyhead{}
\lhead{cj285, bmw227, pmc85, yw344}
\chead{Vault 5431 - Charter}
\rhead{\today}
\fancyfoot{}
\rfoot{\thepage}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\begin{document}
\maketitle
\thispagestyle{empty}

\section{The Team}
\label{sec:the_team}

Here are the team members for the Vault 5431 project:
\begin{description}
  \item[Alicia Wu] (yw344)
  \item[Britney Wong] (bmw227)
  \item[Chang Yang Jiao] (cj285)
  \item[Paul Chesnais] (pmc85)
\end{description}

\section{Weekly Meetings}
\label{sec:weekly_meetings}
We will be meeting on Wednesdays at 5:00 PM and Sundays at 2:00PM.

\section{Proposal}
\label{sec:proposal}

\subsection{Core Vision}
\label{sub:core_vision}

A secure password manager accessible from anywhere, where users can store and access passwords, generate new ones and even store other information, such as product keys and other miscellaneous confidential notes.

\subsection{Key Features}
\label{sub:key_features}
\begin{itemize}
  \item Master password encryption %(Authentication \& Authorization)
  \item Isolated storage %(Confidentiality)
  \item Password Generation
  \item Action logging %(Audit)
  \item Brute force prevention %(Integrity)
  \item Encryption of data on disk and over the network %(Confidentiality \& Integrity)
\end{itemize}

\subsection{Essential Security Elements}
\label{sub:essential_security_elements}

\begin{description}
  \item[Authentication] User be authenticated via their username and master password. No one other than an authenticated and authorized user will have the means to unlock their data store.
  \item[Authorization] Only authorized users will be able to unlock their data store, and add or remove passwords and confidential information. No system administrator will be able to view a user's data store in plaintext.
  \item[Audit] Extensive, timestamped logging of all actions taken by the system, and of all actions taken by users, authenticated or otherwise, in an encrypted log file. All authenticated users will be held accountable for their behavior.
  \item[Confidentiality] The existence of stored information will not be exposed to anyone but the authorized user. Additionally, no information will exposed in plaintext to anyone but said user, including information sent over the network.
  \item[Integrity] A user's data store cannot be changed by actions taken over the network by anyone other than said user.
\end{description}

\section{Abstract}
\label{sec:abstract}

\par The vision of this project is to create a secure password manager that can be accessed by as many devices as possible.

\par A user of Vault 5431 will be able to access his stored passwords and notes by providing a “master password” that serves as the private key to an encryption. After that, the user can see his own information and generate new passwords. The user will only be allowed to have access to his own account and passwords, while no one other than the user will be able to view the information stored in the datastore in plaintext.

\par The system will log all accesses to the password manager to ensure that only authorized and authenticated users have access to their own respective passwords. Suspicious behavior like simultaneous logins from too many IP addresses will also be monitored, and action will be taken when required.

\par A use case is as follows: a user has many online accounts and wishes to have different secure passwords for each account. He needs to safely store them because he cannot remember all of them. By providing users with the ability to generate secure and random passwords and to copy them into their clipboards without seeing them, we provide the first line of defense against key logger and dictionary attacks

\par Another use case is as follows: A user “logs” into Vault 5431 with his master password and is able to see all of his passwords. He then uses them to log into his online accounts.

\end{document}
